Differential invariant signatures for planar Lie group transformations of images

### 2019-12-18 paper/newpaper.tex
todo list

\section{Introduction}
\todo[inline]{
Richard:

Stephen:

}

>>>>

\section{Introduction}
\todo[inline]{
Richard: 
Start on invariant tensor theorem
Generate new pictures, add function details
SE(2) jobs inline
Mobius, Conformal -- finish code, tidy writing
First bash at experimental section

Stephen:
Rearrange examples text to IVT section, write about signatures here
Fix up tables, check bib
Examples for SA(2), A(2) -- need to think about sig here
Moving frame intro
Projective -- tidy writing, especially the names of the invariants
Colour
First bash at conclusion

Later:
Introduction
Count of derivatives and what to say
}
